---
title: "p8105_hw1_qz2492"
author: "Qilin Zheng"
date: "2022-09-24"
output: html_document
---

# Problem 1

```{r penguins dataset}
data("penguins", package = "palmerpenguins")
# Remove NULL value and get the mean flipper length
mean_fl = mean(na.omit(penguins$flipper_length_mm))
```

The data penguins is consisted of `r nrow(penguins)` rows and `r ncol(penguins)`  columns, including *species*, *island*, *bill_length_mm*, *bill_depth_mm*, *flipper_length_mm*, *body_mass_g*, *sex*, and *year*.  
*species* is consisted of _Adelie_, _Chinstrap_ and _Gentoo_, and _island_ is consisted of _Biscoe_, _Dream_ and _Torgersen_. 
From the data we can know the mean flipper length is `r round(mean_fl, digits = 2)`mm.
```{r make a scatter plot and save it}
library(tidyverse)
# Convert to factor variable
penguins$species = factor(penguins$species)
# Make a scatter plot
sc_plot = ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
# Save the plot
ggsave("sc_plot.png")
```

# Problem 2
```{r dataframe}
# Generate the data frame
random_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  char_vec = c('a', 'b', 'c', 'd', 'e', 'f', 'g', 'h', 'i', 'j'),
  fac_vec = factor(c('h', 'h', 'h', 'm', 'm', 'm', 'm', 'l', 'l', 'l'), levels = c('h', 'm', 'l'))
)
# Calculate the mean value of each column
mean_n_s = mean(random_df %>% pull(norm_samp))
mean_n_s_p = mean(random_df %>% pull(norm_samp_pos))
mean_c_V = mean(random_df %>% pull(char_vec)) # didn't work
mean_f_v = mean(random_df %>% pull(fac_vec)) # didn't work
```

```{r function of as.numeric, eval=FALSE}
as.numeric(random_df %>% pull(norm_samp_pos))
as.numeric(random_df %>% pull(char_vec))
as.numeric(random_df %>% pull(fac_vec))
```
The logical vector and factor vector are successfully converted to numeric variables, I think this is because they have some ordinal connections so that R can express it through numbers. But the character vector is converted to NAs, which is due to its disorder.  
But basically, the failure to take the mean value is owing to the variable type.
